\documentclass[12pt]{article}
\usepackage{caption}
\usepackage{float}
\usepackage{graphicx}
\usepackage{fancyhdr}
\pagestyle{fancy}
\pagenumbering{Roman}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}
\setlength{\headheight}{25pt}
\rhead{\textbf{Lightning Coalition Robotics}}
\cfoot{}
\rfoot{\thepage}
\begin{document}

December 8, 2018 - Griffin Dugan

\section{Our Plan:} 
\begin{itemize}
	\item Choose a collection method.
	\item Add arms to the robot.
	\item Clean up wires on the robot.
	\item Get robot's driving methods fixed.
\end{itemize}

We plan to choose which type of collection method. Then we plan to add the collection method to the robot along with all the other arms. We want to clean up the wires on the robot. Then we also want to get our robot's autonomous driving fixed as it has a few errors currently.

\section{What We Got Done:} 
\begin{itemize}
	\item Figured out which type of collection method we would use.
	\item Re-arranged arm to make it better
	\item Got android studio working for everyone
	\item Added the pull up arm to the robot
	\item Chose a collection method.
	\item Cleaned up wires on the robot.
\end{itemize}

Today, we managed to figure out which collection method we would use. We chose our street washing design, where two wheels spin and pull in the blocks. We also re-arranged the arm to be more compact and less heavy as we may add it later on. We also got android studio working for everyone on the team -- or so we hope. We added the pull up arm onto the robot. So now we have a pulling up mechanism. We also cleaned up the wires on our robot. It's much neater now.

\section{What We Didn't Get Done:}
\begin{itemize}
	\item Get robot's driving methods fixed.
\end{itemize}

The only thing we didn't get done was fix the robot's autonomous driving. We think the problem is something with the length data in the code, so we need to give time to work on it so that we can fix it. It drives fine, except for the fact that it sometimes turns much too much.

\section{Next Practice:}
\begin{itemize}
	\item Get robot's driving methods fixed.
	\item Fully fix up the collection method.
	\item Finish autonomous.
\end{itemize}

The next practice is Saturday, December 15th, 2018.
Next practice, we plan to get the robot's autonomous finished. This includes fixing the robot's autonomous driving. Also, we need to fully finish adding the collection wheels to the robot, so that we can test our design fully.

\end{document}