\documentclass[12pt]{article}
\usepackage{caption}
\usepackage{float}
\usepackage{graphicx}
\usepackage{fancyhdr}
\pagestyle{fancy}
\pagenumbering{Roman}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}
\setlength{\headheight}{25pt}
\rhead{\textbf{Lightning Coalition Robotics}}
\cfoot{}
\rfoot{\thepage}
\begin{document}

December 20th, 2018 - Griffin Dugan

\section{Our Plan:}
\begin{itemize}
	\item Design a holder for minerals.
	\item Set up the stronk boi.
	\item Fix the arm.
	\item Code a piece to move a motor.
\end{itemize}

Our plan for today is to design a holder for the minerals, set up the stronk boi, and fix the arm. We have added the stronk boi to the robot, but we need to make it work. We also decided to fix the arm so that it is smaller.  Our coders are planning on coding a piece of code to move a motor a certain distance at a certain speed.

\section{What We Got Done:} 
\begin{itemize}
	\item Set up the stronk boi. (kind of)
	\item Fixed the arm.
	\item Coded a piece to move a motor.
\end{itemize}

We did some coding for the autonomous, we fixed the arm, and we kind of set up the stronk boi. The stronk boi was added to the robot but the string wasn't strong enough.

\section{What We Didn't Get Done:} 
\begin{itemize}
	\item Get the stronk boi working.
	\item Finish the holder for minerals.
\end{itemize}

We need a better type of string to fix the stronk boi up to get it working. It is a key part of our robot. We also need to finish 3D designing the holder for the minerals.

\section{Next Practice:}
\begin{itemize}
	\item Fix stronk boi
	\item Work on autonomous
	\item Finish the holder for minerals.
\end{itemize}

The next practice is December 22nd, 2018.
We need to fix the stronk boi; this may need to happen on the practice after next due to the builder of it not being here. We need to finish the autonomous for the competition that will happen on the 12th of January. We also need to finish the holder for minerals.

\end{document}