\documentclass[12pt]{article}
\usepackage{caption}
\usepackage{float}
\usepackage{graphicx}
\usepackage{fancyhdr}
\pagestyle{fancy}
\pagenumbering{Roman}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}
\setlength{\headheight}{25pt}
\rhead{\textbf{Lightning Coalition Robotics}}
\cfoot{}
\pagenumbering{Roman}
\setcounter{page}{8}
\rfoot{\thepage}
\begin{document}

January 6th, 2019 - Griffin Dugan

\section{Our Plan:}
\begin{itemize}
	\item we plan to restring the Stronk Boi
	\item fine tune autonomous to sense the orientation images in the arena and move better
	\item fix code
	\item work on mineral holding device
\end{itemize}

We plan to restring the stronk boi with Paracord. We want to fine tune the autonomous so that it can move through the field much better. We need to fix the code. We also need to work on the mineral holding device.

\section{What we did:}
\begin{itemize}
	\item Restrung the stronk boi
	\item Worked on fine tuning the autonomous
	\item Worked on mineral holding device
\end{itemize}

This practice, we were able to restring the stronk boi with Paracord, now it works a lot better. We worked on fine tuning the autonomous, but it's not completely perfect currently. W also attempted to add the mineral holder, but we weren't able to add it fully quite yet due to us not having sides to the holder.

\section{What we didn't do:}
\begin{itemize}
	\item Fix code
\end{itemize}

We weren't able to fully fix the code yet. We had a few errors happen, like a servo start smoking. We still need to work on fixing the code.

\section{Next Practice:}
\begin{itemize}
	\item Add sides for the mineral picker.
	\item Finish code
	\item Get ready for the competition.
\end{itemize}

Our next practice is on Friday the 11th of January. We need to get the robot completely working since we have our first competition the day after this next practice. We need to make sure that everything is working well \textit{enough}. Hopefully, it will go well.

\end{document}