\documentclass[12pt]{article}
\usepackage{caption}
\usepackage{float}
\usepackage{graphicx}
\usepackage{fancyhdr}
\pagestyle{fancy}
\pagenumbering{Roman}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}
\setlength{\headheight}{25pt}
\rhead{\textbf{Lightning Coalition Robotics}}
\cfoot{}
\rfoot{\thepage}
\begin{document}

% Add date (e.g. September 14, 2018) and then your name/all authors.
November 2, 2018 - Dylan Donaldson

\section{Our Plan:} % Pretty self explanatory... In this section explain the team's plan.
\begin{itemize}
% After \item, add what you want for the bullet point. (\item adds a new bullet point when you run out.)
	\item Move items to one room to another at the beginning of class
	\item Continuing to assemble lunar lander
	\item Continuing to assemble the arm

\end{itemize}

% Now add a paragraph explaining your plan. You should reference the bullet points above.
On this day, we had to move items to another room which was Ms. Portifields room. Once the team got settled, a group was continuing to assemble the lunar lander. Dylan, Anna, Sarah, and Mimi were assembling the lunar lander.  Another group was continuing to assemble the arm. Sherry and Zoe were the ones that were assembling the arm.  

\section{What We Got Done:} % Just like the above, explain what the team got done during practice.
\begin{itemize}
% After \item, add what you want for the bullet point. (\item adds a new bullet point when you run out.)
	\item We did not get anything done, because this day was hectic because we had to move to another room.
\end{itemize}

% Now add a paragraph explaining what you got done and the reasons behind it. You should reference the bullet points above.
Nothing got done. Since the next day was an open house for the school, we decided to show off the robotics to the visitors and explain how robotics isn't just about the mechanical side of things, it also has a networking side.
\section{What We Didn't Get Done:} % Explain what the team didn't get done during practice.
\begin{itemize}
% After \item, add what you want for the bullet point. (\item adds a new bullet point when you run out.)
	\item Did not finish assembling the lunar lander
	\item Did not finish assembling the arm
\end{itemize}


 
% Now add a paragraph explaining what you didn't get done and the reasons behind it. You should reference the bullet points above.

We did not finish assembling the lunar lander and the arm because we had to move to  another room. 



\section{Next Practice:}
\begin{itemize}
% After \item, add what you want for the bullet point. (\item adds a new bullet point when you run out.)
	\item Finish lander
	\item Finish arm
	\item Build the course
\end{itemize}

% Now add a paragraph explaining what the plan for next practice should be. You should reference the bullet points above.
% And then continue the paragraph.. 
The next practice is Thursday, November 8th, 2018. Our plan for next class is to finish the lunar lander and the arm. Then our next plan is to build the course for the robot. 



\end{document}



