\documentclass[12pt]{article}
\begin{document}

September 13th, 2018 - Griffin Dugan

\section{Our Plan:}
\begin{itemize}
	\item Introduce the team.
	\item Help out the new people.
	\item Brainstorm!
\end{itemize}

Our plan for today is to get the team started and working together. Since we have a bunch of new people on the team, we need to get them understanding the FTC system. Also, we need to do some brainstorming.

\section{What we did:}
\begin{itemize}
	\item Introduced the team.
	\item Helped out new people.
\end{itemize}

We started out the practice by introducing the team to everyone else. Then we watched the FTC challenge video so that we understood what we would have to do. Then we made a rough plan for this season. After that, we left it open to the new team members to ask questions about FTC and the challenge.

\section{What we didn't do:}
\begin{itemize}
	\item Brainstorm...
\end{itemize}

The questions from the new team members took longer than we had expected, so we weren't able to start brainstorming. 

\section{Next Practice:}
\begin{itemize}
	\item Make a plan for practices.
	\item Isolate the parts that we should focus on.
	\item BRAINSTORM!
	\item Start building/coding.
\end{itemize}

Our next practice is on Friday the 21st of September. Next week, we want to create a plan for all of the practices that will happen outside of school. Then we want to isolate the certain parts of the challenge that we can work on; this will help as build the robot quicker. After that, we want to finally get around to brainstorming. And hopefully, we want to get around to starting to build and code.

\end{document}